Adaptative neigbouring methods applied to telephonic base stations

### 2024-08-20 article.tex
Modification 3-NN

Moreover, to simplify the problem, each \acrshort{bs} will be classified in one of this four categories:
\begin{itemize}
    \item \emph{city center};
    \item \emph{urban area};
    \item \emph{extra-urban area};
    \item \emph{countryside}.
\end{itemize}

@@

\subsubsection{$3$-NN mean distance}
For our use case, we need a more specific method. Here is the explanation of how it works:

For each base station $i$, the mean distance to its three nearest neighbours is calculated (we will call this value $\gamma_i$, in 
$\unit{km}$). According to the value of $\gamma_i$, the base station can either be classified as part of one of the categroies of 
Table~\ref{table:crit_summary} (very low value for city center, slighlty higher value for urban area, \dots).

To make this method work properly, only \acrshort{bs} from one provider have to be kept into the calculation process.

Moreover, this values are working well on France but it is not proven that it can work in another country. If someone uses this methods, 
values could be modified [dire que c'est plutot qqch à faire dans le futur et pas que c'est pas vérifié].

[Rajouter les catégories]

@@

>>>>

@@

\subsubsection{$3$-NN mean distance}
For each base station $i$, the mean distance to its three nearest neighbours is calculated (we will call this value $\gamma_i$, in 
$\unit{km}$). According to the value of $\gamma_i$, the base station can either be classified as part of one of the categroies of 
Table~\ref{table:crit_summary}:
\begin{itemize}
    \item city center: $\gamma_i\in [0,1]$;
    \item urban area: $\gamma_i\in ]1,2]$;
    \item extra-urban: $\gamma_i\in ]2,4]$;
    \item countryside: $\gamma_i\in ]4,\infty[$.
\end{itemize}

To make this method work properly, only \acrshort{bs} from the same provider have to be kept into the calculation process.

Althought, this values are working well on France, we haven't tried yet on another country.

@@

\subsection{Measurement of \acrshort{bs} density}
